Main Analysis for Biracial Grade Retention Project

### 2022-09-08 analysis/analysis_main.Rmd
Add example of new graphical approach for model 0, Black/White case

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

```{r calc-cond-means, warning=FALSE}
coef_table_mod0 <- calculate_marg_means(model0)
```

@@

```{r example-plot, fig.cap="Probability of being behind grade for biracial black/white respondents in comparison to their monoracial comparison groups. 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level"}
g <- coef_table_mod0 %>%
  filter(mrace=="Black/White") %>%
  ggplot(aes(x=term, y=estimate, color=multiracial,
             ymin=estimate-1.386*se, ymax=estimate+1.386*se))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.386*se_mid,
                ymax=estimate_mid+1.386*se_mid, fill=multiracial), 
            color=NA, alpha=0.2)+
  geom_linerange(data=subset(coef_table_mod0, multiracial & mrace=="Black/White"))+
  geom_point()+
  coord_flip()+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=c("grey40","red"))+
  scale_fill_manual(values=c("grey40","red"))+
  scale_linetype_manual(values=c(3,1))+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="predicted probability of being behind expected grade")

g+annotate("text", 1, 0.036, hjust="left",
             label="Grey bands give 83.4%\nconfidence interval around\nmonoracial estimates")+
  annotate("text", 2, 0.0445, hjust="left",
             label="Red band gives 83.4%\nconfidence interval around\nmidpoint estimate")+
  annotate("text", 2.3, 0.0365, hjust="left",
             label="Biracial estimate shown\nin red with 83.4% confidence\ninterval")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
color_choices <- c("#003f5c","#58508d","#bc5090","#ff6361","#000000","#ffa600")
```

@@

```{r calc-cond-means, warning=FALSE}
results_mod0 <- calculate_marg_means(model0)
```

@@

```{r example-plot, fig.cap="Probability of being behind grade for biracial black/white respondents in comparison to their monoracial comparison groups. Non-overlap in color-coded confidence bands roughly indicates statistically significant difference at the 5% level"}
results_mod0$coef_table %>%
  filter(mrace=="Black/White") %>%
  ggplot(aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower,
                ymax=upper, fill=colors), color=NA, alpha=0.2)+
  geom_linerange(data=filter(results_mod0$ci_df, mrace=="Black/White"), 
                 position=position_dodge2(width = 0.05), size=1.2,
                 aes(ymin=lower, ymax=upper, color=colors))+
  geom_point(size=2)+
  coord_flip()+
  scale_y_continuous(labels = scales::percent)+
  scale_color_manual(values=color_choices[c(2,5:6)])+
  scale_fill_manual(values=color_choices[c(2,5:6)])+
  labs(x=NULL,
       y="predicted probability of being behind expected grade")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())
```
